### 2013-03-24 doc/sosp13/tasks.tex
fixed TODO in tasks

Each scheduler has three queues:

@@

\TODO{don;t we have an actual queue for higher priority system workers?}

Whenever a task yields or suspends, the scheduler makes a decision about what
to do next. Servicing communication requests (system worker) is given priority
to ensure responsiveness, but to minimize overhead should context switches be
frequent, servicing is performed only if sufficient time has elapsed. Second,
the scheduler determines if any workers with running tasks are ready to
execute; if so, one is scheduled. Finally, if there are no workers ready to
run, but there are tasks waiting to be matched with workers, an idle worker is
woken (or a new worker is spawned), matched with a task, and scheduled.

>>>>

Each scheduler has four queues:

@@

\noindent {\it deadline task queue}, a priority queue of tasks that are executed according to task-specific deadline constraints.

Whenever a task yields or suspends, the scheduler makes a decision about what to do next. First, any task in the deadline task queue who's deadline constraint is met is chosen for execution.  This queue manages high priority system tasks, such as periodically servicing communication requests.  Second, the scheduler determines if any workers with running tasks are ready to execute; if so, one is scheduled. Finally, if there are no workers ready to run, but there are tasks waiting to be matched with workers, an idle worker is woken (or a new worker is spawned), matched with a task, and scheduled.
